Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-03-26 project/stats/true_mem.tex
[ADD] performance tests with and without qrcodes

		\addplot[smooth,color=blue] table[x expr=\thisrowno{0}-25,y index=1] {false/res_7_mongod.csv};
		\addlegendentry{Mongod}

		\addplot[smooth,color=red] table[x expr=\thisrowno{0}-25,y index=1] {false/res_67_kurento-media-server.csv};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=green] table[x expr=\thisrowno{0}-25,y index=1] {false/res_35_kurento-repo.csv};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=magenta] table[x expr=\thisrowno{0}-25,y index=1] {false/res_233_bash.csv};
		\addlegendentry{Java}

>>>>

		\addplot[smooth,color=blue] table[x expr=\thisrowno{0}-112,y index=1] {true/res_7_mongod.csv};
		\addlegendentry{Mongod}

		\addplot[smooth,color=red] table[x expr=\thisrowno{0}-112,y index=1] {true/res_67_kurento-media-server.csv};
		\addlegendentry{Kurento Media Server}

		\addplot[smooth,color=green] table[x expr=\thisrowno{0}-112,y index=1] {true/res_35_kurento-repo.csv};
		\addlegendentry{Kurento Repository}

		\addplot[smooth,color=magenta] table[x expr=\thisrowno{0}-112,y index=1] {true/res_233_bash.csv};
		\addlegendentry{Java}

### 2016-03-26 tese2/13_implementation_model.tex
[ADD] performance tests with and without qrcodes

During a group conversation it is possible to tag points in time for making it easy to access that time either by searching or sharing with other users.

A time tag contains a title, the correspondent group identification number and the time itself.

@@

        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{TimeTag}}                   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ title & Text                           \\ 
            $\medbullet$ time & Date                           \\ \hline

>>>>

During a group conversation it is possible to create time annotations for making it easy to access that time either by searching or sharing with other users.

A time annotation contains a title, the correspondent group identification number and the time itself.

@@

        \begin{tabular}{|ll|}
            \hline
            \multicolumn{2}{|c|}{\textbf{TimeAnnotation}}                   \\ \hline
            $\Diamondblack$ \underline{id}  & ObjectId                      \\ 
            $\medbullet$ groupId            & ObjectId                         \\ 
            $\medbullet$ title & Text                           \\ 
            $\medbullet$ time & Date                           \\ \hline

### 2016-03-26 tese2/16_implementation_content.tex
[ADD] performance tests with and without qrcodes

	\subsection{Tags creation}

	Tags are simpler way save points in time and share them with other users. When a user enters in a conference room the server sends all tags so they can be displayed directly into the user timeline. Each time a tag is created all users are advertised so they can update their interfaces.

@@

	Users can easily search for tags and contents and travel to their correspondent times. In the case of hyper content after handling the result from database we ignore \ac{HTML} tags, extract the text with \emph{Jsoup}\footnote{\url{http://jsoup.org/} (Accessed 21 March 2016)} and apply the query again. We extract the text from \ac{HTML} because accidentatly searching for text contained in \ac{HTML} tags would lead to incorrect results.

>>>>

	\subsection{Time annotations creation}

	Time annotations are simpler way save points in time and share them with other users. When a user enters in a conference room the server sends all annotations so they can be displayed directly into the user timeline. Each time annotation is created all users are advertised so they can update their interfaces.

@@

	Users can easily search for annotations and contents and travel to their correspondent times. In the case of hyper content after handling the result from database we ignore \ac{HTML} tags, extract the text with \emph{Jsoup}\footnote{\url{http://jsoup.org/} (Accessed 21 March 2016)} and apply the query again. We extract the text from \ac{HTML} because accidentatly searching for text contained in \ac{HTML} tags would lead to incorrect results.
